Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-01 ms.tex
somme analysis of residuals after model subtraction.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
The residual is shown with a different scaling below.
In this fitting process, no adjustments were made for timing, which is apparent in the residuals.}\label{fig:kepPCA}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_after_shifted_model.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
(Bottom Left) The residual is shows some periodic behavior.
(Bottom Right) If we allow for shifting in the model with cross-correlation, the periodic behavior is even stronger.
This is likely an erroneous alias caused by a an early typo in the phase grid of 30 seconds instead of 30 minutes.}\label{fig:riverPlots}
\end{centering}
\end{figure*}
